---
title: "Data Wrangling"
format: html
editor: visual
---

```{r}
library(tidyverse)
library(robotstxt)
library(rvest)
library(dplyr)
library(stringr)

```

## Public Approval

1.  Checking whether the page allows scraping

```{r}
pa_url <- "https://www.presidency.ucsb.edu/statistics/data/george-w-bush-public-approval"

# 2. Confirm bots are allowed to access the page 
paths_allowed(pa_url)
```

2.  Retrieve the information (I used AI to create a csv file (public approval.csv))

```{r}
public_approval <- read_csv("public approval.csv")

public_approval$`Start Date` <- as.Date(public_approval$`Start Date`, format = "%m/%d/%Y")
public_approval$`End Date`   <- as.Date(public_approval$`End Date`, format = "%m/%d/%Y")

#add a middle day for easier plotting of graph
public_approval <- public_approval |>
  mutate(Date = `Start Date` + (`End Date` - `Start Date`) / 2)

#pivot table for plotting of graph
public_approval <- public_approval |> 
  pivot_longer(cols = 3:5,
               names_to = "Sentiment",
               values_to = "Percentage_Share"
               )

saveRDS(public_approval, file = "public_approval.rds")
```

## Transcripts of George W Bush's Speeches

1.  Check whether the website allows scraping

```{r}
speech_url <- "https://millercenter.org/the-presidency/presidential-speeches"

paths_allowed(speech_url)
```

2.  For millercenter.org, in order to see the transcripts, we have to click view transcript button for it to appear. As a result, in order to scrape the transcripts, we have to automate the process of clicking so that the transcripts can appear and then scrape it.

```{r}
speech_urls <- c(
  "https://millercenter.org/the-presidency/presidential-speeches/january-15-2009-farewell-address-nation",
  "https://millercenter.org/the-presidency/presidential-speeches/january-12-2009-final-press-conference",
  "https://millercenter.org/the-presidency/presidential-speeches/november-13-2008-speech-financial-markets-and-world-economy",
  "https://millercenter.org/the-presidency/presidential-speeches/january-28-2008-state-union-address",
  "https://millercenter.org/the-presidency/presidential-speeches/january-23-2007-state-union-address",
  "https://millercenter.org/the-presidency/presidential-speeches/january-31-2006-state-union-address",
  "https://millercenter.org/the-presidency/presidential-speeches/february-2-2005-state-union-address",
  "https://millercenter.org/the-presidency/presidential-speeches/september-3-2004-remarks-republican-national-convention",
  "https://millercenter.org/the-presidency/presidential-speeches/january-20-2004-state-union-address",
  "https://millercenter.org/the-presidency/presidential-speeches/january-28-2003-state-union-address",
  "https://millercenter.org/the-presidency/presidential-speeches/june-6-2002-address-nation-department-homeland-security",
  "https://millercenter.org/the-presidency/presidential-speeches/september-20-2001-address-us-response-attacks-september-11",
  "https://millercenter.org/the-presidency/presidential-speeches/may-11-2001-proposal-global-fund-fight-hivaids-malaria-and",
  "https://millercenter.org/the-presidency/presidential-speeches/january-20-2001-first-inaugural-address"
)

speech_text <- lapply(
  speech_urls,
  function(url) {
    read_html(url) |>
      html_elements(".view-transcript p") |>
      html_text2() |>
      paste(collapse = " ")
  }
)

SpeechData <- tibble(
  url = speech_urls,
  text = unlist(speech_text),
  title = speech_urls |>
    basename() |>
    str_replace_all("-", " ") |>
    str_to_title()
)

```

```{r}
SpeechData <- SpeechData |> mutate(date = word(title,1,3))
SpeechData$date <- SpeechData$date |> as.Date(date, format = "%B %d %Y")

saveRDS(SpeechData, file = "SpeechData.rds")
```

### Sources:

**Data set**

American Presidency Project. (n.d.). George W. Bush public approval. University of California, Santa Barbara. <https://www.presidency.ucsb.edu/statistics/data/george-w-bush-public-approval>

Miller Center. (n.d.). *Presidential Speeches Collection*. University of Virginia. Retrieved from <https://millercenter.org/the-presidency/presidential-speeches>
